Photovoltaic System Reconfiguration Strategy For Mismatch Condition\\ {\footnotesize \textsuperscript{}}

### 2018-10-09 main.tex
Update main.tex

To execute a power simulation, we have to assign panels to each string to realize a candidate configuration. However, the way is not given in \cite{b10} and some candidate configurations are infeasible. 
The definition of feasibility in (\ref{feas}). When a configuration needs working modules in a string (\textit{$M_S$}) are less than number of working module per-string (\textit{$Q_{M_{n}}$}), then this configuration is infeasible. 
\begin{equation}
\left\{\begin{matrix}
M_S < Q_{M_{n}} & & \text{Infeasible}\\ 
M_S \geqslant Q_{M_{n}} & & \text{Feasible} 
\label{feas}
\end{matrix}\right. 
\end{equation}
For an configuration example [C2] \{0.5A, 0.5A, 2A\}, there are 8 PV modules working on each string. According to Table I, for a string current on 2A at least need 4 panels, remaining panels can not provide enough PV module working on 0.5A for another two strings. 
Of course we can compute it by using an exhaustive search. However, it is time-consuming. So, we need an algorithm to efficiently identify feasibility of a configuration and realize the configuration if it is feasible.

@@

%\begin{equation}
%\begin{aligned}
%\textit{MPP candidates} = [\{ 0.5, 0.5, 2\}, \{0.5, 2, 2\}, \{2, 2, 2\}, \{2, 2, 3\}]
%\end{aligned}\label{mpp}
%\end{equation}
%\begin{equation}
%\begin{aligned}
%\textit{$Q_{M_n}$} = &  [\{8, 8, 8\}, \{7, 7, 7\}, \{5, 5, 5\}, \{4, 4, 4\}]
%\end{aligned}
%\label{qmn}
%\end{equation}
\section{An Algorithm to Identify Feasibility}
In this section, we propose an algorithm to identify feasibility.
\subsection{The Input And Output Of Algorithm}

>>>>

To execute a power simulation, we need assign panels into different strings to realize a configuration. However, the way to assign panels is not given in \cite{b10} and some configuration candidates are infeasible. 
The definition of feasibility in (\ref{feas}). When a configuration needs working modules in a string (\textit{$M_S$}) are less than number of working module per-string (\textit{$Q_{M_{n}}$}), then this configuration is infeasible. 
\begin{equation}
\left\{\begin{matrix}
M_S < Q_{M_{n}} & & \text{Infeasible}\\ 
M_S \geqslant Q_{M_{n}} & & \text{Feasible} 
\label{feas}
\end{matrix}\right. 
\end{equation}
For an configuration example [C2] \{0.5A, 0.5A, 2A\}, there are 8 PV modules working on each string. According to Table I, for a string current on 2A at least need 4 panels, remaining panels can not provide enough PV module working on 0.5A for another two strings. 
Of course we can compute it by using an exhaustive search. However, it is time-consuming. So, we need an algorithm to efficiently identify feasibility of a configuration and realize the configuration if it is feasible.

@@

%\begin{equation}
%\begin{aligned}
%\textit{MPP candidates} = [\{ 0.5, 0.5, 2\}, \{0.5, 2, 2\}, \{2, 2, 2\}, \{2, 2, 3\}]
%\end{aligned}\label{mpp}
%\end{equation}
%\begin{equation}
%\begin{aligned}
%\textit{$Q_{M_n}$} = &  [\{8, 8, 8\}, \{7, 7, 7\}, \{5, 5, 5\}, \{4, 4, 4\}]
%\end{aligned}
%\label{qmn}
%\end{equation}
\section{An Algorithm to Identify Feasibility}
In this section, we propose an algorithm to identify feasibility of configuration candidates.
\subsection{The Input And Output Of Algorithm}
